Initial Analysis

### 2019-08-21 Initial_Analysis.Rmd
Removed all models from data_path of all computers

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/All_Models/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

# The function
EstTransIndex_All <- function(Spp,Model,Neighbors,Coord,Save="Y"){

@@

@@

# Set Spceies list
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
  filter(!TaxonKey %in% Species_List)

# Step to run function for species not computed
Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))

Exploited_Species <- Exploited_Species %>%
  filter(!TaxonKey %in% Computed_Spp)

# For Function
Exploited_Species_List <- Exploited_Species$TaxonKey[1:3]

@@

# NUmber of cores to us 
# n_cores <- detectCores()

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
    )
  )
)

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  Data_Path <- "Z:/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
  }
if(Sys.info()[7] == "carmelia"){
  Data_Path <- "~/GitHub/FishForVisa/Temporal_Data/"
  Path <- paste(Data_Path,sep = "")
}
if(Sys.info()[7] == "hall1000"){
  Data_Path <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/"
  Path <- paste(Data_Path,"Results/",sep = "")
}

@@

#### For testing 
# Spp <- 600059
 #Model <- "All"
 #Neighbors <- Neighbor_List
 #Coord = CoorG
# __________________________________

@@

  # MODEL INDEX (TRESHOLDS 1 & 2) #
  Model_Index_D <- Trans_Spp %>% 
    group_by(Name,
             TaxonKey,
             Model_Index
    ) %>% 
    summarise(n_cells_spp = n()) %>% 
    select(-n_cells_spp)

@@

# Set Spceies list
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep="")) %>%
  filter(TaxonKey %in% Species_List)

# Step to run function for species not computed
# Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))

# Exploited_Species <- Exploited_Species %>%
  #filter(!TaxonKey %in% Computed_Spp)

# For Function
Exploited_Species_List <- Exploited_Species$TaxonKey

@@

# Number of cores to us 
n_cores <- detectCores()-8

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN = EstTransIndex, Model = "All", Neighbors = Neighbor_List, Coord = CoorG
    )
  )
)
